Verifying Cache Coherence Protocols for an Infinite Family of Cache Hierarchies

### 2014-02-06 paper/Introduction.tex
probably fixed one comment

Formal verification of cache coherence protocols has traditionally been done
using model checking. That family of analyses significantly restricts the size
as well as complexity of the system that has to be verified; most model-checking
based approaches can not handle more than one level of hierarchy. To the best of
our knowledge, the largest system that has been verified using model checking
has only 12 processors~\cite{Chen:2008:VHC:1559300}, in an era when many
observers are predicting mainstream systems with hundreds of processor cores.

>>>>

Formal verification of cache coherence protocols has traditionally been done
using model checking. That family of analyses significantly restricts the size
as well as complexity of the system that has to be verified; most model-checking
based approaches can not handle more than one level of hierarchy. To the best of
our knowledge, the largest system that has been verified using model checking
has only 12 processors\xxx{the comment was meant to cite other papers from this paper as well. anyways i will take a crack at it}~\cite{Chen:2008:VHC:1559300}, in an era when many
observers are predicting mainstream systems with hundreds of processor cores.
